\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\PassOptionsToPackage{hyphens}{url}
\usepackage{url}
\usepackage[breaklinks=true]{hyperref}
\Urlmuskip=0mu plus 1mu

\begin{document}

\section*{Poster References}

\begin{enumerate}
    \item McAtee, P. et al. (2013) 'A dynamic interplay between phytohormones is required for fruit development, maturation, and ripening', \textit{Frontiers in Plant Science}, 4. Available at: \url{https://doi.org/10.3389/fpls.2013.00079}.

    \item Fernández-Cancelo, P. et al. (2022) 'Ethylene and abscisic acid play a key role in modulating apple ripening after harvest and after cold-storage', \textit{Postharvest Biology and Technology}, 188, p. 111902. Available at: \url{https://doi.org/10.1016/j.postharvbio.2022.111902}.

    \item Wu, M. et al. (2023) 'Gibberellins involved in fruit ripening and softening by mediating multiple hormonal signals in tomato', \textit{Horticulture Research}, 11(2). Available at: \url{https://doi.org/10.1093/hr/uhad275}.

    \item Agliassa, C. and Maffei, M.E. (2018) 'Origanum vulgare Terpenoids Induce Oxidative Stress and Reduce the Feeding Activity of Spodoptera littoralis', \textit{International Journal of Molecular Sciences}, 19(9), p. 2805. Available at: \url{https://doi.org/10.3390/ijms19092805}.

    \item Unsicker, S.B., Kunert, G. and Gershenzon, J. (2009) 'Protective perfumes: the role of vegetative volatiles in plant defense against herbivores', \textit{Current Opinion in Plant Biology}, 12(4), pp. 479–485. Available at: \url{https://doi.org/10.1016/j.pbi.2009.04.001}.

    \item CHEN, Y. et al. (2022) 'Overexpression of the apple expansin-like gene MdEXLB1 accelerates the softening of fruit texture in tomato', \textit{Journal of Integrative Agriculture}, 21(12), pp. 3578–3588. Available at: \url{https://doi.org/10.1016/j.jia.2022.08.030}.

    \item Matthias Naets et al. (2022) 'Time Is of the Essence—Early Activation of the Mevalonate Pathway in Apple Challenged With Gray Mold Correlates With Reduced Susceptibility During Postharvest Storage', \textit{Frontiers in Microbiology}, 13. Available at: \url{https://doi.org/10.3389/fmicb.2022.797234}.

    \item Guo, Z. et al. (2025) 'Dihydroartemisinic acid dehydrogenase-mediated alternative route for artemisinin biosynthesis', \textit{Nature Communications}, 16(1). Available at: \url{https://doi.org/10.1038/s41467-024-55644-8}.

    \item Tran, L.T. et al. (2021) 'Phenolic Profiling of Five Different Australian Grown Apples', \textit{Applied Sciences}, 11(5), p. 2421. Available at: \url{https://doi.org/10.3390/app11052421}.

    \item Li, Y. et al. (2021) 'Effects of Genetic Background and Altitude on Sugars, Malic Acid and Ascorbic Acid in Fruits of Wild and Cultivated Apples (Malus sp.)', \textit{Foods}, 10(12), p. 2950. Available at: \url{https://doi.org/10.3390/foods10122950}.

    \item Schlathölter, I. et al. (2021) 'Low Outcrossing from an Apple Field Trial Protected with Nets', \textit{Agronomy}, 11(9), p. 1754. Available at: \url{https://doi.org/10.3390/agronomy11091754}.

    \item Zinselmeier, M.H. et al. (2025) 'Towards engineering hybrid incompatibility in plants', \textit{Plant Biotechnology Journal}, 23(7), pp. 2752–2754. Available at: \url{https://doi.org/10.1111/pbi.70096}.

    \item Dobránszki, J. and Teixeira da Silva, J.A. (2010) 'Micropropagation of apple — A review', \textit{Biotechnology Advances}, 28(4), pp. 462–488. Available at: \url{https://doi.org/10.1016/j.biotechadv.2010.02.008}.

    \item Food Standards Agency (no date) \textit{Genetically modified foods}. \\
          Available at: \url{https://www.food.gov.uk/safety-hygiene/genetically-modified-foods#how-gm-foods-are-labelled}.

    \item World Health Organization (2023) \textit{No level of alcohol consumption is safe for our health}. \\
          Available at: \url{https://www.who.int/europe/news/item/04-01-2023-no-level-of-alcohol-consumption-is-safe-for-our-health}.

    \item Directive 2009/41/EC of the European Parliament and of the Council of 6 May 2009 on the contained use of genetically modified micro-organisms (Recast) (Text with EEA relevance) (2026) Legislation.gov.uk. Available at: \url{https://www.legislation.gov.uk/eudr/2009/41/introduction/2020-12-31/data.xht?view=snippet&wrap=true} (Accessed: 10 February 2026).

\end{enumerate}

\end{document}
