\begin{longtable}{|>{\raggedright\arraybackslash}p{0.10\textwidth}|>{\raggedright\arraybackslash}p{0.48\textwidth}|>{\raggedright\arraybackslash}p{0.22\textwidth}|>{\raggedright\arraybackslash}p{0.14\textwidth}|}
    \caption{List of terminators with corresponding sequences, descriptions, and sources.} \\
    \hline
    \textbf{Name} & \textbf{Sequence} & \textbf{Description} & \textbf{Source/Part ID} \\
    \hline
    \endfirsthead

    \hline
    \textbf{Name} & \textbf{Sequence} & \textbf{Description} & \textbf{Source/Part ID} \\
    \hline
    \endhead

    \hline
    \multicolumn{4}{r}{\textit{Continued on next page}}                                    \\
    \endfoot

    \hline
    \endlastfoot

    tNOS &
    {\small\ttfamily\raggedright
            \seqsplit{CGTTCAAACATTTGGCAATAAAGTTTCTTAAGATTGAATCCTGTTGCCGGTCTTGCGATGATTATCATATAATTTCTGTTGAATTACGTTAAGCATGTAATAATTAACATGTAATGCATGACGTTATTTATGAGATGGGTTTTTATGATTAGAGTCCCGCAATTATACATTTAATACGCGATAGAAAACAAAATATAGCGCGCAAACTAGGATAAATTATCGCGCGCGGTGTCATCTATGTTACTAGATCGGG}
            \par}
                      &
    Stands for nopaline synthase terminator. Derived from Agrobacterium tumefaciens and it is a commonly used terminator for expression system in plants.
                      &
    BBa\_K1537031 \\
    \hline

    tOCS &
    {\small\ttfamily\raggedright
            \seqsplit{CTGCTTTAATGAGATATGCGAGACGCCTATGATCGCATGATATTTGCTTTCAATTCTGTTGTGCACGTTGTAAAAAACCTGAGCATGTGTAGCTCAGATCCTTACCGCCGGTTTCGGTTCATTCTAATGAATATATCACCCGTTACTATCGTATTTTTATGAATAATATTCTCCGTTCAATTTACTGATTGTACCCTACTACTTATATGTACAATATTAAAATGAAAACAATATATTGTGCTGAATAGGTTTATAGCGACATCTATGATAGAGCGCCACAATAACAAACAATTGCGTTTTATTATTACAAATCCAATTTTAAAAAAAGCGGCAGAACCGGTCAAACCTAAAAGACTGATTACATAAATCTTATTCAAATTTCAAAAGGCCCCAGGGGCTAGTATCTACGACACACCGAGCGGCGAACTAATAACGTTCACTGAAGGGAACTCCGGTTCCCCGCCGGCGCGCATGGGTGAGATTCCTTGAAGTTGAGTATTGGCCGTCCGCTCTACCGAAAGTTACGGGCACCATTCAACCCGGTCCAGCACGGCGGCCGGGTAACCGACTTGCTGCCCCGAGAATTATGCAGCATTTTTTTGGTGTATGTGGGCCCCAAATGAAGTGCAGGTCAAACCTTGACAGTGACGACAAATCGTTGGGCGGGTCCAGGGCGAATTTTGCGACAACATGTCGAGGCTCAGCA}
            \par}
                      &
    Stands for octopine synthase terminator. It is derived from Agrobacterium tumefaciens. Like NOS, it is also commonly used for transgenic plants.
                      &
    Addgene \#71268 \\
    \hline

    t35S &
    {\small\ttfamily\raggedright
            \seqsplit{CTAGAGTCCGCAAAAATCACCAGTCTCTCTCTACAAATCTATCTCTCTCTATTTTTCTCCAGAATAATGTGTGAGTAGTTCCCAGATAAGGGAATTAGGGTTCTTATAGGGTTTCGCTCATGTGTTGAGCATATAAGAAACCCTTAGTATGTATTTGTATTTGTAAAATACTTCTATCAATAAAATTTCTAATTCCTAAAACCAAAATCCAGTGACC}
            \par}
                      &
    Derived from Cauliflower Mosaic Virus (CaMV). Also deemed to be frequently used in transgenic plants.
                      &
    BBa\_K1159307 \\
    \hline

    tRBCS E9 &
    {\small\ttfamily\raggedright
            \seqsplit{CAGGCCTCCCAGCTTTCGTCCGTATCATCGGTTTCGACAACGTTCGTCAAGTTCAATGCATCAGTTTCATTGCCCACACACCAGAATCCTACTAAGTTTGAGTATTATGGCATTGGAAAAGCTGTTTTCTTCTATCATTTGTTCTGCTTGTAATTTACTGTGTTCTTTCAGTTTTTGTTTTCGGACATCAAAATGCAAATGGATGGATAAGAGTTAATAAATGATATGGTCCTTTTGTTCATTCTCAAATTATTATTATCTGTTGTTTTTACTTTAATGGGTTGAATTTAAGTAAGAAAGGAACTAACAGTGTGATATTAAGGTGCAATGTTAGACATATAAAACAGTCTTTCACCTCTCTTTGGTTATGTCTTGAATTGGTTTGTTTCTTCACTTATCTGTGTAATCAAGTTTACTATGAGTCTATGATCAAGTAATTATGCAATCAAGTTAAGTACAGTATAGGCTTT}
            \par}
                      &
    Stands for ribulose-1,5-bisphosphate carboxylase small subunit (rbcS) gene, clone E9 terminator. Derived from Pisum sativum (peas). Extracted from Plant expression vector pZG159 at position 1882--2176 base pairs.
                      &
    GenBank MW026669.1 \\
    \hline

    tHSP 18.2 &
    {\small\ttfamily\raggedright
            \seqsplit{TATGAAGATGAAGATGAAATATTTGGTGTGTCAAATAAAAAGCTTGTGTGCTTAAGTTTGTGTTTTTTTCTTGGCTTGTTGTGTTATGAATTTGTGGCTTTTTCTAATATTAAATGAATGTAAGATCTCATTATAATGAATAAACAAATGTTTCTATAATCCATTGTGAATGTTTTGTTGGATCTCTTCTGCAGCATATAACTACTGTATGTGCTATGGTATGGACTATGGAATATGATTAAAGATAAG}
            \par}
                      &
    Stands for heat shock protein 18.2 terminator. Derived from Arabidopsis thaliana.
                      &
    Addgene \#68186 \\
    \hline

    tMAS &
    {\small\ttfamily\raggedright
            \seqsplit{CTTGGACTCCCATGTTGGCAAAGGCAACCAAACAAACAATGAATGATCCGCTCCTGCATATGGGGCGGTTTGAGTATTTCAACTGCCATTTGGGCTGAATTGTAGACATGCTCCTGTCAGAAATTCCGTGATCTTACTCAATATTCAGTAATCTCGGCCAATATCCTAAATGTGCGTGGCTTTATCTGTCTTTGTATTGTTTCATCAATTCATGTAACGTTTGCTTTTCTTATGAATTTTCAAATAAATTAT}
            \par}
                      &
    Stands for mannopine synthase terminator. Derived from Agrobacterium tumefaciens.
                      &
    Addgene \#153381 \\
    \hline
\end{longtable}
